Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-03 draft/accordionComplexSurfaces.tex
work on definition construction surface

\centerline{
\begin{tikzpicture}[scale=2, thick]
	\node (s) at (-1,0) {$s(\alpha)$};
	\node (t) at (1,0) {$t(\alpha)$};
	\node (v) at (0,1) {$\green v(\alpha)$};
	\node (vd) at (0,-1) {$\red v\dual(\alpha)$};
	\draw[color=black, ->] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, ->] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
	\draw[color=green, ->] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
	\draw[color=red, ->] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
	\draw[color=red, ->] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
\end{tikzpicture}
}

\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\beta)$, proceed to the following identifications:
    \begin{itemize}
    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
    \end{itemize}
\end{enumerate}
\end{definition}

\begin{example}
\vincent{TODO.}
\end{example}

Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
This surface is actually endowed with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{remark}
Observe that
\begin{itemize}
\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$,
\item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\end{itemize}
A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
\end{remark}

>>>>

\centerline{
\begin{tikzpicture}[
	scale=2,
	thick,
	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=2pt}
	]
	\node[roundNode, label=left:{$s(\alpha)$}] (s) at (-1,0) {};
	\node[roundNode, label=right:{$t(\alpha)$}] (t) at (1,0) {};
	\node[roundNode, fill=green, label=above:{$\green v(\alpha)$}] (v) at (0,1) {};
	\node[roundNode, fill=red, label=below:{$\red v\dual(\alpha)$}] (vd) at (0,-1) {};
	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
\end{tikzpicture}
}

\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\beta)$, proceed to the following identifications:
    \begin{itemize}
    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
    \end{itemize}
\end{enumerate}
The orientations on the edges are only use to perform the identifications and can be immediately forgotten.
\end{definition}

This construction is illustrated on \fref{fig:examplesSurfaces}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for two quivers~$\bar Q$ of \fref{fig:quivers}.}
	\label{fig:examplesSurfaces}
\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item 
\item
\end{itemize}
\vincent{TODO}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{remark}
Observe that
\begin{itemize}
\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$.
\item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\item 
\end{itemize}
\vincent{TODO}
A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
Finally, observe that we could also have constructed the surface
\end{remark}
